A multi-species benchmark for training and validating mass spectrometry proteomics machine learning models

### 2024-08-30 doc/nine-species/response.tex

(1) The author reanalyzed the nine-species dataset using Tide search engine. I highly suggest at least two search engines should be used to make sure the PSMs are correct, since almost every search engine has its own preference.

\response{We agree with you that the choice of search engine introduces a potential bias into the dataset construction.
  However, mitigating this bias is challenging.
  If we combine the results of two different search engine, using either a union or an intersection operation, then we sacrifice the ability to rigorously control the FDR among the reported list of discoveries.}

(2) Why did the author only consider the FDR at PSM level? I think the FDR at protein level is commonly used now.

\response{We agree that, in many settings, controlling the FDR at the protein level is appropriate, especially when a study is aimed at characterizing the protein content of a given set of biological samples.
  However, for constructing a benchmark of PSMs used for training and validating \textit{de novo} sequencing methods, we believe that protein level FDR control is not as relevant.
  In particular, even if we control the FDR at the protein level, the benchmark needs to report a set of PSMs rather than proteins, and it is not clear how to go from a set of detected proteins to a corresponding collection of confident PSMs.
  Consider, for example, the widely used ``picked protein'' method for protein-level FDR control \cite{savitski2015scalable}.
  In the Savitski \textit{et al.}\ (2015) description of this method, each protein is assigned a score equal to the sum of the search engine scores assigned to its peptides.
  With such an approach, a protein can be detected with high confidence even if one or more of its associated peptides has low scores, as long as some of the peptides have very high scores.
  Thus, if we include all PSMs associated with a detected peptide in our benchmark, we risk contaminating the benchmark with incorrect PSMs.

  It is possible that the reviewer is suggesting that we should control the FDR at both the PSM and protein level.
  This approach would have the converse problem: some PSMs that are correctly detected might be discarded if there is insufficient evidence to accept the protein at the specified FDR threshold.
  Ultimately, we are creating a benchmark of PSMs, so PSM-level FDR control seemed the most appropriate.
}

### 2024-09-30 doc/nine-species/nine-species.tex
Added data citation

The dataset contains files resulting from various steps in the generation of the benchmark:
\begin{itemize}
\item Spectrum files in MGF format, produced by ThermoRawFileParser.
\item Reference proteome files in FASTA format, downloaded from UniProt.
\item Search results files for both targets and decoys, in tab-delimited format, produced by Tide.
\item PSM-level Percolator results files for targets, in tab-delimited format.
`\item Annotated MGF \edit{and corresponding mzSpecLib \cite{klein2024proteomics}} files for both versions of the benchmark (main and balanced).
\end{itemize}
Also included are log files for the steps of the analysis pipeline carried out using Crux \cite{park2008rapid} (Tide indexing, Tide search, and Percolator).
The data is available at \url{https://doi.org/10.5281/zenodo.12819175}.

>>>>

The dataset \cite{noble2024benchmark} contains files resulting from various steps in the generation of the benchmark:
\begin{itemize}
\item Spectrum files in MGF format, produced by ThermoRawFileParser.
\item Reference proteome files in FASTA format, downloaded from UniProt.
\item Search results files for both targets and decoys, in tab-delimited format, produced by Tide.
\item PSM-level Percolator results files for targets, in tab-delimited format.
`\item Annotated MGF \edit{and corresponding mzSpecLib \cite{klein2024proteomics}} files for both versions of the benchmark (main and balanced).
\end{itemize}
Also included are log files for the steps of the analysis pipeline carried out using Crux \cite{park2008rapid} (Tide indexing, Tide search, and Percolator).
The data \cite{noble2024benchmark} is available at \url{https://doi.org/10.5281/zenodo.13685813}.
